\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-01-22 doc/chapters/output.tex
reformat a bit and explain user input and heavy self-energies

\begin{align}
  \left(y_u^{\text{\DRbar}}(M_Z)\right)_{ij} &= \frac{\sqrt{2} m_{u,ji}}{v_u} ,\\
  \left(y_d^{\text{\DRbar}}(M_Z)\right)_{ij} &= \frac{\sqrt{2} m_{d,ji}}{v_d} ,\\
  \left(y_e^{\text{\DRbar}}(M_Z)\right)_{ij} &= \frac{\sqrt{2} m_{e,ji}}{v_e} ,
\end{align}
%
where the fermion mass matrices are given by
%
\begin{align}
  m_{u,11} &= m_{u}^{\userinput} ,\\
  m_{u,22} &= m_{c}^{\userinput} ,\\
  m_{u,33} &= m_{t,\text{susy}}^{\text{\DRbar}}(M_Z),\\
  m_{d,11} &= m_{d}^{\userinput} ,\\
  m_{d,22} &= m_{s}^{\userinput} ,\\
  m_{d,33} &= m_{b,\text{susy}}^{\text{\DRbar}}(M_Z),\\
  m_{e,11} &= m_{e}^{\userinput} ,\\
  m_{e,22} &= m_{\mu}^{\userinput} ,\\
  m_{e,33} &= m_{\tau,\text{susy}}^{\text{\DRbar}}(M_Z),\\
  m_{u,ij} &= m_{d,ij} = m_{u,ij} = 0 \quad \forall i \neq j.
\end{align}
%
Only the 3rd generation quark masses are calculated in the \DRbar
scheme from the user input quantities $m_t^\text{pole}$,
$m_{b,\text{SM}}^{\text{\MSbar}}(M_Z)$,
$m_{\tau,\text{SM}}^{\text{\MSbar}}(M_Z)$.  The top quark \DRbar mass
is calculated via
%
\begin{align}
  m_{t,\text{susy}}^{\text{\DRbar}}(\mu) &= m_t^\text{pole}
  + \re\Sigma_{tt}^{S,\text{heavy}}(m_t^\text{pole})
  + m_t^\text{pole} \left[
    \re\Sigma_{tt}^{L,\text{heavy}}(m_t^\text{pole}) +
    \re\Sigma_{tt}^{R,\text{heavy}}(m_t^\text{pole}) +
    \Delta m_t^{(1),\text{qcd}} +
    \Delta m_t^{(2),\text{qcd}}
  \right].
\end{align}
%
The QCD contributions $\Delta m_t^{(1),\text{qcd}}$ and $\Delta
m_t^{(2),\text{qcd}}$ are taken from \cite{Bednyakov:2002sf} and read
%
\begin{align}
  \Delta m_t^{(1),\text{qcd}} &= -\frac{g_3^2 \left(5-3 \log\left(\frac{m_t^2}{\mu^2}\right)\right)}{12 \pi^2},\\
  \Delta m_t^{(2),\text{qcd}} &= \left(\Delta
    m_t^{(1),\text{qcd}}\right)^2 - \frac{g_3^4 \left[396
      \log^2\left(\frac{m_t^2}{\mu^2}\right)-1476
      \log\left(\frac{m_t^2}{\mu^2}\right)-48 \zeta(3)+2011+16 \pi ^2
      (1+\log(4))\right]}{4608 \pi^4}.
\end{align}
%
The \DRbar mass of the bottom quark is calculated via
\cite{Baer:2002ek}
%
\begin{align}
  m_{b,\text{susy}}^{\text{\DRbar}}(\mu) &=
  \frac{m_{b,\text{SM}}^{\text{\DRbar}}(\mu)}{1 -
    \re\Sigma_{bb}^{S,\text{heavy}}(m_{b,\text{SM}}^\text{\MSbar})/m_b
    - \re\Sigma_{bb}^{L,\text{heavy}}(m_{b,\text{SM}}^\text{\MSbar}) -
    \re\Sigma_{bb}^{R,\text{heavy}}(m_{b,\text{SM}}^\text{\MSbar})} ,\\
  m_{b,\text{SM}}^{\text{\DRbar}}(\mu) &=
  m_{b,\text{SM}}^{\text{\MSbar}}(\mu) \left(1 - \frac{\alpha_s}{3
      \pi} - \frac{23}{72} \frac{\alpha_s^2}{\pi^2} + \frac{3
      g_2^2}{128 \pi^2} + \frac{13 g_1^2}{1152 \pi^2}\right) .
\end{align}
%
The \DRbar mass of the $\tau$ is calculated via
%
\begin{align}
  m_{\tau,\text{susy}}^{\text{\DRbar}}(\mu) &=
  m_{\tau,\text{SM}}^{\text{\DRbar}}(\mu) +
  \re\Sigma_{\tau\tau}^{S,\text{heavy}}(m_{\tau,\text{SM}}^\text{\MSbar}) +
  m_{\tau,\text{SM}}^{\text{\DRbar}}(\mu) \left[
    \re\Sigma_{\tau\tau}^{L,\text{heavy}}(m_{\tau,\text{SM}}^\text{\MSbar}) +
    \re\Sigma_{\tau\tau}^{R,\text{heavy}}(m_{\tau,\text{SM}}^\text{\MSbar})
  \right] ,\\
  m_{\tau,\text{SM}}^{\text{\DRbar}}(\mu) &= m_{\tau,\text{SM}}^{\text{\MSbar}}(\mu)
  \left(1 - 3 \frac{g_1^2 - g_2^2}{128 \pi^2}\right).
\end{align}

>>>>

The expressios for the SM-Yukawa coupling matrices extracted from the
tree-level mass matrices of the SM-fermions.  In the MSSM, for
example, they read
%
\begin{align}
  y_u^{\text{\DRbar}}(M_Z) &= \frac{\sqrt{2} m_{u}^T}{v_u} ,\\
  y_d^{\text{\DRbar}}(M_Z) &= \frac{\sqrt{2} m_{d}^T}{v_d} ,\\
  y_e^{\text{\DRbar}}(M_Z) &= \frac{\sqrt{2} m_{e}^T}{v_e}.
\end{align}
%
At the low-scale the fermion mass matrices are composed as
%
\begin{align}
  m_u =
  \begin{pmatrix}
    m_{u}^{\userinput} & 0 & 0 \\
    0 & m_{c}^{\userinput} & 0 \\
    0 & 0 & m_{t,\text{susy}}^{\text{\DRbar}}(M_Z)
  \end{pmatrix} ,\\
  m_d =
  \begin{pmatrix}
    m_{d}^{\userinput} & 0 & 0 \\
    0 & m_{s}^{\userinput} & 0 \\
    0 & 0 & m_{b,\text{susy}}^{\text{\DRbar}}(M_Z)
  \end{pmatrix} ,\\
  m_e =
  \begin{pmatrix}
    m_{e}^{\userinput} & 0 & \\
    0 & m_{\mu}^{\userinput} & 0 \\
    0 & 0 & m_{\tau,\text{susy}}^{\text{\DRbar}}(M_Z)
  \end{pmatrix}.
\end{align}
%
Only the 3rd generation quark masses are calculated in the \DRbar
scheme from the user input quantities $m_t^\text{pole}$,
$m_{b,\text{SM}}^{\text{\MSbar}}(M_Z)$,
$m_{\tau,\text{SM}}^{\text{\MSbar}}(M_Z)$.  In detail, the top quark
\DRbar mass is calculated via
%
\begin{align}
  \begin{split}
    m_{t,\text{susy}}^{\text{\DRbar}}(\mu) &= m_t^\text{pole} +
    \re\Sigma_{tt}^{S,\text{heavy}}(m_t^\text{pole}) \\
    &\phantom{=\;} + m_t^\text{pole}
    \left[ \re\Sigma_{tt}^{L,\text{heavy}}(m_t^\text{pole}) +
      \re\Sigma_{tt}^{R,\text{heavy}}(m_t^\text{pole}) + \Delta
      m_t^{(1),\text{qcd}} + \Delta m_t^{(2),\text{qcd}} \right] ,
  \end{split}
\end{align}
%
where the $\Sigma_{ff}^\text{heavy}$ denotes the self-energy of
fermion $f$ without the Standard Model contributions.  The appearing
QCD corrections $\Delta m_t^{(1),\text{qcd}}$ and $\Delta
m_t^{(2),\text{qcd}}$ are taken from
\cite[Eq. (58),(61)]{Bednyakov:2002sf} and read
%
\begin{align}
  \Delta m_t^{(1),\text{qcd}} &= -\frac{g_3^2 \left(5-3 \log\left(\frac{m_t^2}{\mu^2}\right)\right)}{12 \pi^2},\\
  \begin{split}
    \Delta m_t^{(2),\text{qcd}} &= \left(\Delta
      m_t^{(1),\text{qcd}}\right)^2 \\
    &\phantom{=\;} - \frac{g_3^4 \left[396
        \log^2\left(\frac{m_t^2}{\mu^2}\right)-1476
        \log\left(\frac{m_t^2}{\mu^2}\right)-48 \zeta(3)+2011+16 \pi
        ^2 (1+\log 4)\right]}{4608 \pi^4}.
  \end{split}
\end{align}
%
The \DRbar mass of the bottom quark is calculated via
\cite{Baer:2002ek}
%
\begin{align}
  m_{b,\text{susy}}^{\text{\DRbar}}(\mu) &=
  \frac{m_{b,\text{SM}}^{\text{\DRbar}}(\mu)}{1 -
    \re\Sigma_{bb}^{S,\text{heavy}}(m_{b,\text{SM}}^\text{\MSbar})/m_b
    - \re\Sigma_{bb}^{L,\text{heavy}}(m_{b,\text{SM}}^\text{\MSbar}) -
    \re\Sigma_{bb}^{R,\text{heavy}}(m_{b,\text{SM}}^\text{\MSbar})} ,\\
  m_{b,\text{SM}}^{\text{\DRbar}}(\mu) &=
  m_{b,\text{SM}}^{\text{\MSbar}}(\mu) \left(1 - \frac{\alpha_s}{3
      \pi} - \frac{23}{72} \frac{\alpha_s^2}{\pi^2} + \frac{3
      g_2^2}{128 \pi^2} + \frac{13 g_1^2}{1152 \pi^2}\right) ,
\end{align}
%
where $m_{b,\text{SM}}^{\text{\MSbar}}(M_Z)$ is user input.  The
\DRbar mass of the $\tau$ is calculated via
%
\begin{align}
  \begin{split}
    m_{\tau,\text{susy}}^{\text{\DRbar}}(\mu) &=
    m_{\tau,\text{SM}}^{\text{\DRbar}}(\mu) +
    \re\Sigma_{\tau\tau}^{S,\text{heavy}}(m_{\tau,\text{SM}}^\text{\MSbar}) \\
    &\phantom{=\;} + m_{\tau,\text{SM}}^{\text{\DRbar}}(\mu) \left[
      \re\Sigma_{\tau\tau}^{L,\text{heavy}}(m_{\tau,\text{SM}}^\text{\MSbar})
      +
      \re\Sigma_{\tau\tau}^{R,\text{heavy}}(m_{\tau,\text{SM}}^\text{\MSbar})
    \right] ,
  \end{split}\\
  m_{\tau,\text{SM}}^{\text{\DRbar}}(\mu) &= m_{\tau,\text{SM}}^{\text{\MSbar}}(\mu)
  \left(1 - 3 \frac{g_1^2 - g_2^2}{128 \pi^2}\right),
\end{align}
%
where $m_{\tau,\text{SM}}^{\text{\MSbar}}(M_Z)$ is user input.
